\thetitle

### 2022-06-24 thesis/paper.tex
next par in korean

The literature on admissions markets also includes a vast body of research on the deferred acceptance algorithm, an algorithm for matching students to schools having finite capacities that generalizes the Gale--Shapley algorithm for stable marriage. The algorithm takes students' ordinal preferences over schools and schools' ordinal preferences over students as input, and produces an assignment that possesses a number of desirable properties: It is a stable matching, meaning that no student--school pair is incentivized to deviate from the assignment. And the preference-reporting mechanism is incentive compatible, meaning that no student can improve her outcome by lying about her preferences (Gale and Shapley 1962; Roth 1982). In design, deferred acceptance is a centralized assignment algorithm; however, stable assignment also be interpreted as the equilibrium of a decentralized admissions game in which agents have perfect information about one another's preferences (Azevedo and Leshno 2016).

>>>>

\ifen
The literature on admissions markets also includes a vast body of research on the deferred acceptance algorithm, an algorithm for matching students to schools having finite capacities that generalizes the Gale--Shapley algorithm for stable marriage. The algorithm takes students' ordinal preferences over schools and schools' ordinal preferences over students as input, and produces an assignment that possesses a number of desirable properties: It is a stable matching, meaning that no student--school pair is incentivized to deviate from the assignment. And the preference-reporting mechanism is incentive compatible, meaning that no student can improve her outcome by lying about her preferences (Gale and Shapley 1962; Roth 1982). In design, deferred acceptance is a centralized assignment algorithm; however, stable assignment also be interpreted as the equilibrium of a decentralized admissions game in which agents have perfect information about one another's preferences (Azevedo and Leshno 2016).
\else
입학 시장을 모형화한 문헌은 학교 배정 알고리즘에 관한 연구도 포함하며, 유한한 용량으로 갖춘 학교로 학생을 배정하는 deferred acceptance (DA) 알고리즘은 대표적인 사례다. DA는 Gale--Shapley의 안정 결혼(stable marriage) 알고리즘의 확장으로, 학생과 학교의 서로 대한 선호 순위를 입력하면 이 알고리즘이 출력하는 배정 계획은 몇 가지 바람직한 성질을 가진다. 우선, DA의 출력은 안정 매칭(stable matching)이므로 어떤 학생--학교 쌍도 주어진 배정을 위반할 동기가 없음을 보일 수 있다. 그리고 DA에서 학생이 선호 순위를 신청하는 방법은 유인 부합적(incentive compatible)인 것이며, 학생이 자신의 선호를 부정적으로 나타내어 더 좋은 학교로 배정받을 수 없다고 의미한다 (Gale과 Shapley 1962; Roth 1982). DA는 원래 중앙에서 진행하는 학교 배정 알고리즘으로 설계되었지만, 안정 매칭은 모든 참여자에게 다른 참여자의 선호 순위가 완벽하게 알려진 분산적 입학 게임의 균형으로 해석할 수도 있다 (Azevedo와 Leshno 2016). 
\fi
